Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis

### 2023-03-31 manuscript.Rmd
do the paper

  group_names <- unique(data[ , group])

@@

  model_coef <- bind_rows(
    tidy(model.overall, conf.level = .95) %>% mutate(model = "overall"), 
    tidy(model.group1, conf.level = .95) %>% mutate(model = "group1"), 
    tidy(model.group2, conf.level = .95) %>% mutate(model = "group2"), 
    tidy(model.configural, conf.level = .95) %>% mutate(model = "configural"), 
    tidy(model.metric, conf.level = .95) %>% mutate(model = "metric"), 
    tidy(model.scalar, conf.level = .95) %>% mutate(model = "scalar"), 
    tidy(model.strict, conf.level = .95) %>% mutate(model = "strict")
  )

  model_fit <- bind_rows(
    glance(model.overall) %>% mutate(model = "overall"), 
    glance(model.group1) %>% mutate(model = "group1"), 
    glance(model.group2) %>% mutate(model = "group2"), 
    glance(model.configural) %>% mutate(model = "configural"), 
    glance(model.metric) %>% mutate(model = "metric"), 
    glance(model.scalar) %>% mutate(model = "scalar"), 
    glance(model.strict) %>% mutate(model = "strict")
    )

@@

```{r test-function, eval = F, include = F}
# temp test
data_coef = results.large.res$model_coef
model_step = "configural" 
item_name = "q4"
x_limits = c(-1,1)
y_limits = c(min(df.large.res$q4), max(df.large.res$q4))
ci_level = .95
model_results = results.invariant$model.configural
lv_name = "lv"

@@

```{r eval = F, echo = T, include = T, size = "small"}
plot_mgcfa(
  data_coef = results.invariant$model_coef, # output from model_coef
  model_step = "configural", # which model do you want to plot
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # latent variable limits to graph
  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.invariant$model.configural, # what model results do you want 
  lv_name = "lv" # which latent variable do you want 
)
```

@@

Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$). Therefore, the latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on. The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four. The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`. The ribbon bands around the plotted slopes indicate the confidence interval for that estimate. In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.

@@

The item intercepts ($b_0$) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero. These are represented by a dot with a set of confidence error bars around the point. The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`. In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different. You can use `y_limits` to zoom in on the graph if these are too small to be distinguishable.

@@

Residuals are trickier to plot, as they are the left over error when predicting the observed variables $\epsilon$. It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate. Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot. The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`). The distributions are plotted to represent the normal spread of values using the standard error of the residuals. The violin plot allows for direct comparison of those residuals and their potential distributions. Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.

@@

```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
plot_mgcfa(
  data_coef = results.invariant$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.invariant$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

@@

The latent means in Figure \@ref(fig:large-load-pic) do appear to show differences, albeit visually small. The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal). In the simulated model, the *only* manipulated parameter is question 4's loading. In real models, the differences may be larger due to other variation found in the parameter estimates. Therefore, once you discover items you believe would make a model "partially" invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items. Additionally, consider that we set the scaling of the model to 0. The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means. The practical implications of this difference will depend on the research and interpretations of the researcher.

```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.small.load$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.med.load$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.large.load$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

For intercepts, the small (Figure \@ref(fig:small-int-pic)), medium (Figure \@ref(fig:med-int-pic)), and large (Figure \@ref(fig:large-int-pic)) depictions represent $d_{MACS}$ values of `r apa_num(d_small_int)$DMACS[4]`, `r apa_num(d_med_int)$DMACS[4]`, and `r apa_num(d_large_int)$DMACS[4]`, respectively. Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well). Note how little the intercept differences appear to influence the latent variable means and distributions.

```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.small.int$model_coef, # output from model_coef
  model_step = "metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.med.int$model_coef, # output from model_coef
  model_step = "metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.large.int$model_coef, # output from model_coef
  model_step = "metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

@@

```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.small.res$model_coef, # output from model_coef
  model_step = "scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.med.res$model_coef, # output from model_coef
  model_step = "scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.large.res$model_coef, # output from model_coef
  model_step = "scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

@@

@aiena2014 examined the RS-14 [@wagnild2009] exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample. Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups. @aiena2014 did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations.

```{r echo = T, include = T, size = "small"}
load("RS14.Rdata")
model.rs <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"
results.rs <- mgcfa(data = DF, 
                    group = "sample", 
                    model = model.rs)

results.rs$model_fit %>% select(model, AIC, BIC, cfi, tli, rmsea, srmr)

##write out partial codes
partial_syntax <- paste(colnames(DF)[1:14], "~1") #all columns again 
partial_syntax

@@

plot_mgcfa(
  data_coef = partial.coef,
  model_step = "intercepts", 
  item_name = "RS6",
  x_limits = c(-1,1),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  model_results = partial.rs.2.picture, 
  ci_level = .95,
  lv_name = "RS"
)

>>>>

  group_names <- unique(data[ , group])
  data$group <- data[ , group]

@@

  model_coef <- bind_rows(
    tidy(model.overall, conf.level = .95) %>% mutate(model = "Overall"), 
    tidy(model.group1, conf.level = .95) %>% mutate(model = "Group 1"), 
    tidy(model.group2, conf.level = .95) %>% mutate(model = "Group 2"), 
    tidy(model.configural, conf.level = .95) %>% mutate(model = "Configural"), 
    tidy(model.metric, conf.level = .95) %>% mutate(model = "Metric"), 
    tidy(model.scalar, conf.level = .95) %>% mutate(model = "Scalar"), 
    tidy(model.strict, conf.level = .95) %>% mutate(model = "Strict")
  )

  model_fit <- bind_rows(
    glance(model.overall) %>% mutate(model = "Overall"), 
    glance(model.group1) %>% mutate(model = "Group 1"), 
    glance(model.group2) %>% mutate(model = "Group 2"), 
    glance(model.configural) %>% mutate(model = "Configural"), 
    glance(model.metric) %>% mutate(model = "Metric"), 
    glance(model.scalar) %>% mutate(model = "Scalar"), 
    glance(model.strict) %>% mutate(model = "Strict")
    )

@@

```{r test-function, eval = F, include = F}
# temp test
data_coef = results.large.res$model_coef
model_step = "Configural" 
item_name = "q4"
x_limits = c(-1,1)
y_limits = c(min(df.large.res$q4), max(df.large.res$q4))
ci_level = .95
model_results = results.invariant$model.configural
lv_name = "lv"

@@

```{r eval = F, echo = T, include = T, size = "small"}
plot_mgcfa(
  data_coef = results.invariant$model_coef, # output from model_coef
  model_step = "Configural", # which model do you want to plot
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # latent variable limits to graph
  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.invariant$model.configural, # what model results do you want 
  lv_name = "lv" # which latent variable do you want 
)
```

@@

Factor loadings represent the slope of the regression equation for the latent variable predicting the scores on the observed variable ($\hat{Y} \sim b_0 + b_1X + \epsilon$). Therefore, the latent variable is shown on the x-axis using standardized values (i.e., *z*-scores) where -1 indicates one standard deviation below the mean for the latent variable, 0 indicates the mean for the latent variable and so on. The y-axis indicates the observed variable scores, and here, the plot includes the entire range of the scale of the data for item four. The coefficient ($b_1$) for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "=~") %>% slice_tail() %>% pull(estimate))`. The ribbon bands around the plotted slopes indicate the confidence interval for that estimate. In this plot, while the coefficients for each group are not literally equal, the overlapping and parallel slope bands indicate they are not different practically.

@@

The item intercepts ($b_0$) are plotted on the middle line where they would cross the y-axis at a latent variable score of zero. These are represented by a dot with a set of confidence error bars around the point. The intercept for group 1 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, while the coefficient for group 2 was `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`. In this invariant depiction, the overlap in the intercepts is clear, indicating they are not different. You can use `y_limits` to zoom in on the graph if these are too small to be distinguishable.

@@

Residuals are trickier to plot, as they are the left over error when predicting the observed variables $\epsilon$. It is tempting to plot this value as the confidence band around the slope, however, that defeats the purpose of understanding that the slopes are estimated separately from the residuals, and both have an associated variability around their parameter estimate. Therefore, residuals are represented in the inset picture at the bottom right of the item invariance plot. The black bars represent the estimated residual for each group (group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_head() %>% pull(estimate))`, group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("q4", term)) %>% filter(op == "~~") %>% slice_tail() %>% pull(estimate))`). The distributions are plotted to represent the normal spread of values using the standard error of the residuals. The violin plot allows for direct comparison of those residuals and their potential distributions. Note that the placement has nothing to do with the x or y-axis and is designed to always show in the same location, regardless of size/value.

@@

```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
plot_mgcfa(
  data_coef = results.invariant$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.invariant$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

@@

The latent means in Figure \@ref(fig:large-load-pic) do appear to show differences, albeit visually small. The latent means diagram shows the impact of any group differences that aren't constrained, and this image shows the configural model (as the metric model would force them to be equal). In the simulated model, the *only* manipulated parameter is question 4's loading. In real models, the differences may be larger due to other variation found in the parameter estimates. Therefore, once you discover items you believe would make a model "partially" invariant, you may wish to estimate that model and graph the item again using the partially invariant model to see only the effect of the non-invariant items. Additionally, consider that we set the scaling of the model to 0. The estimate for the lv mean in the large loading model was group 1: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate))`, and group 2: `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))`, which results in `r apa_num(results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_head() %>% pull(estimate) - results.invariant$model_coef %>% filter(model == "Configural") %>% filter(grepl("lv", term)) %>% filter(op == "~1") %>% slice_tail() %>% pull(estimate))` difference in group means. The practical implications of this difference will depend on the research and interpretations of the researcher.

```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.small.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.med.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.large.load$model_coef, # output from model_coef
  model_step = "Configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

For intercepts, the small (Figure \@ref(fig:small-int-pic)), medium (Figure \@ref(fig:med-int-pic)), and large (Figure \@ref(fig:large-int-pic)) depictions represent $d_{MACS}$ values of `r apa_num(d_small_int)$DMACS[4]`, `r apa_num(d_med_int)$DMACS[4]`, and `r apa_num(d_large_int)$DMACS[4]`, respectively. Intercept differences can be clearly seen represented by the spacing out of the intercept locations (and thus, the overall line as well). While the changes in intercept do not appear to change the latent means, the cavaet to this simulation is that only item four was manipulated. An example is provided below that demonstrates large changes in latent means.

```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.small.int$model_coef, # output from model_coef
  model_step = "Metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.med.int$model_coef, # output from model_coef
  model_step = "Metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.large.int$model_coef, # output from model_coef
  model_step = "Metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

@@

```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.small.res$model_coef, # output from model_coef
  model_step = "Scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.med.res$model_coef, # output from model_coef
  model_step = "Scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.large.res$model_coef, # output from model_coef
  model_step = "Scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

@@

@aiena2014 examined the RS-14 [@wagnild2009] exploring the factor structure of the Resiliency Scale in a clinical sample receiving treatment services and a college student sample. Measurement invariance was calculated for differences separately for these samples for gender and race finding a partially invariant models with a few item intercepts or residuals that differed between groups. @aiena2014 did not compare the clinical to the student sample for measurement invariance, and it is reasonable to expect potential differences in these two populations. This example will demonstrate the procedure for researchers who wish to use partial invariance steps and how to interpret real, messy data.

```{r echo = T, include = T, size = "small"}
# load the data
load("RS14.Rdata")
# build the one-factor model 
model.rs <- "RS =~ RS1+RS2+RS3+RS4+RS5+RS6+RS7+RS8+RS9+RS10+RS11+RS12+RS13+RS14"
# run the multi-group CFA
results.rs <- mgcfa(data = DF, 
                    group = "sample", 
                    model = model.rs)
```

```{r eval = F, echo = T, include = T, size = "small"}
# how to get results in table 
results.rs$model_fit %>% 
        select(model, AIC, BIC, cfi, tli, rmsea, srmr)
```

```{r rs-table, results = 'asis'}
apa_table(results.rs$model_fit %>% 
        select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
        col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for RS-14 Example")
```

Table \@ref(fig:invariant-pic) indicates the results after running the one-factor model. There are several guidelines for assessing assessing a degradation in model fit [@cheung]

```{r}
##write out partial codes
partial_syntax <- paste(colnames(DF)[1:14], "~1") #all columns again 
partial_syntax

@@

plot_mgcfa(
  data_coef = partial.coef,
  model_step = "intercepts", 
  item_name = "RS6",
  x_limits = c(-2,2),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  model_results = partial.rs.2.picture, 
  ci_level = .95,
  lv_name = "RS"
)

plot_mgcfa(
  data_coef = partial.coef,
  model_step = "intercepts", 
  item_name = "RS7",
  x_limits = c(-2,2),
  y_limits = c(min(DF$RS7), max(DF$RS7)),
  model_results = partial.rs.2.picture, 
  ci_level = .95,
  lv_name = "RS"
)

SD <- tapply(DF$RS6, DF$sample, sd)
M <- tapply(DF$RS6, DF$sample, mean)
N <- tapply(DF$RS6, DF$sample, length)

SD2 <- tapply(DF$RS7, DF$sample, sd)
M2 <- tapply(DF$RS7, DF$sample, mean)
N2 <- tapply(DF$RS7, DF$sample, length)

library(MOTE)
d.ind.t(M[1], M[2], SD[1], SD[2], N[1], N[2])
d.ind.t(M2[1], M2[2], SD2[1], SD2[2], N2[1], N2[2])
lavaan_dmacs(partial.rs.2.picture, "Clinical")
lavaan_dmacs(results.rs$model.configural, "Clinical")
```

6: Drive

7: Perseverance

I1tems for the RS–14 are described in the measure’s manual (Wagnild, 2009a)
and can be viewed at www.resiliencecenter.com.
